### 2014-06-05 writing/S'14 paper/discussion.tex
First minor tweaks from the review session.
Intermediate paper update

This paper evaluated two RNNs in a series of three increasingly
challenging interpretive tasks involving natural language inference:
the core relational algebra of natural logic with entailment and
exclusion; recursive propositional logic structures; and statements
involving quantification and negation. The results suggest that RNTNs,
but not plain RNNs, have the capacity to meet the challenges of these
tasks with reasonably-sized training sets. These positive results are
promising for the future of learned representation models in the
applied modeling of compositional semantics.

Of course, challenges remain. In terms of our experimental data, even
the RNTN falls short of perfection in our more complex tasks, with
performance falling off steadily as the depth of recursion grows. It
remains to be seen whether these deficiencies can be overcome with
improvements to the model, the optimization procedures, or the
linguistic representations
\cite{sochergrounded,kalchbrenner2014convolutional}. In addition,
there remain subtle questions about how to fairly assess whether these
models have truly generalized in the way we want them to. There is a
constant tension between giving the models training data that gives
them a chance to learn the target logical functions and revealing the
answer to them in a way that leads to overfitting. The underlying
logical theories provide only limited guidance on this point. Finally,
we have only scratched the surface of the logical complexity of
natural language; in future experiments, we hope to test sentences
with embedded quantifiers, multiple interacting quantifiers, relative
clauses, and other kinds of recursive structure. Nonetheless, the
rapid progress the field has made with these models in recent years
provides ample reason to be optimistic that they can be trained to
meet the challenges of natural language semantics.

>>>>

This paper evaluated two recursive models in a series of three increasingly
challenging interpretive tasks involving natural language inference:
the core relational algebra of natural logic with entailment and
exclusion; recursive propositional logic structures; and statements
involving quantification and negation. The results suggest that RNTNs,
but not plain RNNs, have the capacity to meet the challenges of these
tasks with reasonably-sized training sets. These positive results are
promising for the future of learned representation models in the
applied modeling of compositional semantics.

Of course, challenges remain. In terms of our experimental data, even
the RNTN falls short of perfection in our more complex tasks, with
performance falling off steadily as the depth of recursion grows. It
remains to be seen whether these deficiencies can be overcome with
improvements to the model, the optimization procedures, or the
linguistic representations
\cite{sochergrounded,kalchbrenner2014convolutional}. In addition,
there remain subtle questions about how to fairly assess whether these
models have truly generalized in the way we want them to. There is a
constant tension between giving the models training data that gives
them a chance to learn the target logical functions and revealing the
answer to them in a way that leads to overfitting. The underlying
logical theories provide only limited guidance on this point, and the fact that 
there is a finite universe of possible expressions makes this an unavoidable issue. 
Finally, we have only scratched the surface of the logical complexity of
natural language; in future experiments, we hope to test sentences
with embedded quantifiers, multiple interacting quantifiers, relative
clauses, and other kinds of recursive structure. Nonetheless, the
rapid progress the field has made with these models in recent years
provides ample reason to be optimistic that they can be trained to
meet the challenges of natural language semantics.

### 2014-06-05 writing/S'14 paper/recursion.tex
Intermediate paper update

\begin{figure}[htp]
  \centering
  \includegraphics[width=5.5in]{recursion\string_results\string_updated.eps}
  \caption{Model performance on propositional logic, by expression size.}  
  \label{prop-results}
\end{figure}

@@

\begin{figure}[htp]
  \centering
  \includegraphics[width=5.5in]{recursion\string_pairwise.eps}
  \caption{...}  
  \label{prop-results}
\end{figure}

>>>>

\begin{figure}[htp]
  \centering
  \includegraphics[width=5.5in]{recursion\string_results\string_updated.eps}
  \caption{Model performance on propositional logic, by expression size. The dashed line indicates that only expressions of size four or less appeared in the training data.}  
  \label{prop-results}
\end{figure}

@@

In an attempt to better understand the limited success of the RNN model, we discovered that this model looses information about in longer statements in a particularly problematic way. It appears that that model is unable to distinguish between two sentences when the only difference between those sentences is embedded within a very deep structure. We evaluated both models on sentences that differed in only one term, but for which that one term was embedded under a large number of conjunctions, such as the pair \ii{a (and a)} and \ii{a (and b)}, or the pair \ii{a (and (a (and a)))} and \ii{a (and (a (and b)))}. We then measured the Euclidean distance between the vector representations of the two sentences in each pair. Our findings are shown in Figure~\ref{prop-falloff}, and show that while the RNTN can distinguish the two sentences well at every size that we test, the RNN fails after a depth of approximately six.

\begin{figure}[htp]
  \centering
  \includegraphics[width=5.5in]{recursion\string_pairwise.eps}
  \caption{How well each model can distinguish to expressions that differ by one term, measured for terms embedded under different numbers of tokens of \ii{and}.}  
  \label{prop-falloff}
\end{figure}
